Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-30 02_Paper/paper.tex
Chapter 3
ideas for introduction

@@

In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
\AP{ 
       - How does the previous sentences apply to the democell?
       - This suits better in the methods section}

>>>>

Product features such as reliability and durability or complete functionality determine to a large extent the success and profit of a company on the market.
In addition, product quality is a company's showcase. Therefore, the established standard must be ensured by careful quality assurance.
Traditional methods of quality control, such as 100\% control, may conflict with other production goals, such as production speed and low reject rates.
When choosing the right quality control tools, a compromise must be made in most cases. For example, a higher production speed requires statistical quality control. Statistical methods, however,
do not provide one hundred percent certainty that the required product quality will be achieved.
A new approach based on quality prediction using ML algorithms provides a remedy here.

@@

In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}. %This sentence can be deleted if needed.
In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....). % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
\AP{ 
       - How does the previous sentences apply to the democell?
       - This suits better in the methods section}
       - Review
